The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-03-11 paper.tex
update

\documentclass[twocolumn]{aastex631}
\usepackage{mathtools}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{txfonts}
\usepackage{lipsum, babel}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{xcolor,colortbl}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{url}
\usepackage{floatrow}
\usepackage[]{subfigure}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{empheq}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{mathrsfs}
\usepackage{soul}
\pdfminorversion=5

@@

\section{Methodology}
\label{Methodology}
  We used the GPU-accelerated special relativistic hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
  National Taiwan University\
  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
  to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.

@@

 The fiducial run (a1-a3) with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 with a semiminor axis about 6.8 kpc on the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles\
 based on X-ray emissions.

@@

 The most interesting finding is that there are innermost bubbles\
 (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\

@@

 \Cref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,
 including pressure (top), temperature (middle), density (bottom) with the same jet source as the fiducial run\
 but in different Galactic environments.

 %To explore how the disk affects the formation of the Galactic bubbles,\
 We compare the fiducial run (a1-a3)\
 with the case adopting the smooth disc\
 (b1-b3), specified by the initial density profile shown in
 \Cref{fig__initial-density-profile}, in a stratified atmosphere.\
 The results show that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (c1-c3) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, the two rightmost columns reveal that the development of the innermost bubbles\
 is always associated with the disc, without the disc,\
 the outermost bubbles and the turbulent plasma will be oblique,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg.png}
    \caption{
             The slices of pressure (top), temperature (middle), and number density (bottom)\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (a1-a3)\
             and the smooth disc (b1-b3) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
             in an uniform atmosphere (c1-c3) is spherical-shape,\
             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
             Also, the two rightmost columns reveal that the development of the innermost bubbles\
             is always associated with the disc, without the disc (d1-d3),\
             the outermost bubbles and the turbulent plasma will be oblique,
             indicating the dense disc is crucial for\
             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg}
  \end{figure}

\begin{figure}%
  \centering%
  \subfigure[][]%
    {%
      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
      \label{fig__jetI5+ismSeed3-45deg-a}% A
    }%
  \hspace{2pt}%
  \subfigure[][]%
    {%
      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
      \label{fig__jetI5+ismSeed3-45deg-b}%
    }%
  \hspace{2pt}%
  \subfigure[][]%
    {%
      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
      \label{fig__jetI5+ismSeed3-45deg-c}%
    }%
  \hspace{2pt}%
  \subfigure[][]%
    {%
      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-d}
      \label{fig__jetI5+ismSeed3-45deg-d} %D
    }%
  \caption{}%
  \label{fig__jetI5+ismSeed3-45deg}%
\end{figure}%

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
    \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of the profiles in the yellow band.\
             The sharp pressure jump at $z=3.62$ kpc\
             indicates that the innermost bubbles\
             (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
             are an expanding reverse shock.
     }
    \label{fig__profile}
  \end{figure}

@@

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
               Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
               and observed from the solar system.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray-map}
  \end{figure*}

>>>>

\documentclass[twocolumn]{aastex631}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{txfonts}
\usepackage{lipsum, babel}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{xcolor,colortbl}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{url}
\usepackage{floatrow}
\usepackage[]{subfigure}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{empheq}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{mathrsfs}
\usepackage{soul}
\pdfminorversion=5

\renewcommand*{\thesubfigure}{\Alph{subfigure}}

@@

\section{Methodology}
\label{Methodology}
  We used the GPU-accelerated special relativistic\
  hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
  National Taiwan University\
  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
  to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.

@@

 The fiducial run (\Cref{fig__jetI5+ismSeed3-45deg-a})\
 with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 with a semiminor axis about 6.8 kpc on the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020}\
 for modeling the eROSITA bubbles\
 based on X-ray emissions.

@@

 The most interesting finding is that there are innermost bubbles\
 (dashed box in the top panel of \Cref{fig__jetI5+ismSeed3-45deg-a})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\

@@

 \Cref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,\
 including pressure (top), temperature (middle),\
 density (bottom) with the same jet source as the fiducial run\
 but in different Galactic environments.

 %To explore how the disk affects the formation of the Galactic bubbles,\
 We compare the clumpy disk (\Cref{fig__jetI5+ismSeed3-45deg-a})\
 with the smooth disc (\Cref{fig__jetI5+ismSeed3-45deg-b}),\
 specified by the initial density profile shown in \Cref{fig__initial-density-profile},\
 in a stratified atmosphere.\
 The results show that the initial density distribution of\
 the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (\Cref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, \Cref{fig__jetI5+ismSeed3-45deg-c,fig__jetI5+ismSeed3-45deg-d}\
 reveal that the development of the innermost bubbles\
 is always associated with the disc, without the disc,\
 the outermost bubbles and the turbulent plasma will be oblique,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.

\begin{figure}%
  \centering%
  \subfigure[][]%
    {%
      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
      \label{fig__jetI5+ismSeed3-45deg-a}%
    }%
  \hspace{2pt}%
  \subfigure[][]%
    {%
      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
      \label{fig__jetI5+ismSeed3-45deg-b}%
    }%
  \hspace{2pt}%
  \subfigure[][]%
    {%
      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
      \label{fig__jetI5+ismSeed3-45deg-c}%
    }%
  \hspace{2pt}%
  \subfigure[][]%
    {%
      \includegraphics[height=10.1cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
      \label{fig__jetI5+ismSeed3-45deg-d}%
    }%
  \caption{
             The slices of pressure (top), temperature (middle), and number density (bottom)\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (column a)\
             and the smooth disc (column b) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
             in an uniform atmosphere (column c) is spherical-shape,\
             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
             Also, the two rightmost columns reveal that the development of the innermost bubbles\
             is always associated with the disc, without the disc (column d),\
             the outermost bubbles and the turbulent plasma will be oblique,
             indicating the dense disc is crucial for\
             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
  }%
  \label{fig__jetI5+ismSeed3-45deg}%
\end{figure}%

\begin{figure}%
  \centering%
  \subfigure[][]%
    {%
      \includegraphics[height=7cm]{figures/fig__profile-1.png}%
      \label{fig__profile-1}%
    }%
  \hspace{2pt}%
  \subfigure[][]%
    {%
      \includegraphics[height=7cm]{figures/fig__profile-2.png}%
      \label{fig__profile-2}%
    }%
    \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of the profiles in the yellow band.\
             The sharp pressure jump at $z=3.62$ kpc\
             indicates that the innermost bubbles\
             (dashed box in the top panel in \Cref{fig__jetI5+ismSeed3-45deg-a})\
             are an expanding reverse shock.
     }
    \label{fig__profile}
  \end{figure}

@@

  \begin{figure*}[]
    \subfigure[(A) Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6--1.0 keV range.\
               Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
               and observed from the solar system.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[(B) Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray-map}
  \end{figure*}
